Performance for the masses: Experiments with A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2016-02-03 GECCO/volunteer-clouds-gecco16.tex
This will try to be the last change. Uploading
Reducing it to 8 pages again
We are on the edge, @fergunet. Every time you make a change you should check that it does not push it over the page limit.

Specifically, this experiment was deployed in a virtual private server with 512MB of memory
running Ubuntu OS version 14.04 and hosted in DigitalOcean.com. Unlike previous
experiments where the optimum was expected to be found many times, 
this problem was expected to constantly run for many days finding only
sub-optimal approximations. In order to achieve this, the only change needed 
in the framework was to limit the number of chromosomes kept in the pool. 
Previously, every PUT request which included a new chromosome increased 
the size of the pool. But in a long-running experiment this has to be avoided
in order to not exhaust the available memory. In this experiment the size
of a chromosome was 1000 double precision numbers, so that considering this
and the memory available in the server, the pool was limited 
to 10,000 chromosomes.  In order to keep this size
constant, a random chromosome was pulled out of the pool before inserting a
new one, when the pool was full. For this problem {\sf NodEO}'s {\tt chromosome-float} 
and {\tt classic-ea-float} modules were used. The parameters for the EA 
were tournament size = 3 and  population size = 500, returning exchanging a
chromosome with the server every 100 generations. Again, there were two workers in each window.
As in previous experiments, a few calls to participation were published on social networks.

@@

Another area is how to enhance the number and quality of
volunteers. For instance, adding a bit of more
control to the user might contribute also to gamification. Right now
the user has only two Web Workers. It is a matter of a single click to
open more tabs in the browser, giving more Web Workers, but it would be
interesting to put everything in a single page and under our control,
to check how often this happens and under which conditions.

>>>>

Specifically, this experiment was deployed in a virtual private server with 512MB of memory
running Ubuntu OS version 14.04 and hosted in DigitalOcean.com. Unlike previous
experiments where the optimum was expected to be found many times, 
this problem was expected to constantly run for many days finding only
sub-optimal approximations. In order to achieve this, the only change needed 
in the framework was to limit the number of chromosomes kept in the pool. 
Previously, every PUT request which included a new chromosome increased 
the size of the pool. But in a long-running experiment this has to be avoided
in order to not exhausting the available memory. In this experiment the size
of a chromosome was 1000 double precision numbers, so that considering this
and the memory available in the server, the pool was limited 
to 10,000 chromosomes.  In order to keep this size
constant, a random chromosome was pulled out of the pool before inserting a
new one, when the pool was full. For this problem {\sf NodEO}'s {\tt chromosome-float} 
and {\tt classic-ea-float} modules were used. The parameters for the EA 
were tournament size = 3 and  population size = 500, returning exchanging a
chromosome with the server every 100 generations. Again, there were two workers in each window.
As in previous experiments, a few calls to participation were published on social networks.

@@

Other improvements could include adding a bit of more
control to the user might contribute also to gamification. Right now
the user has only two Web Workers. It is a matter of a single click to
open more tabs in the browser, giving more Web Workers, but it would be
interesting to put everything in a single page and under our control,
to check how often this happens and under which conditions.
